More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-11 2016-Weak-FH-Bisim/WeakBisim.tex
corrections
Proof lemma 6 in progress
work in progress

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~~and~~}
%\[
Q\models{\openrule
	{
		\beta_j^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\TODO{important comment added:}
Note that this does not mean that any two pNets can be composed and produce an open 
transition. Indeed, the predicate $\Pred\land\Pred\land \alpha_Q=\beta_{j_0}$ is not 
be satisfiable if the action of $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
Note also that $\beta_{j_0}$ is now only used as an intermediate term inside formulas: it 
does not appear neither as global action nor as an action of a hole.
\begin{small}

@@

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $\gamma_{j_0}=[\beta_0..\beta_n]$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n(\alpha_p= \beta_p\land \Pred_p) \qquad\text{and~}
\Post=\Post\,'\uplus \bigotimes_{p=0}^n
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

@@

\noindent We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^{1a}_p},  
				{\Post^{1a}_p}}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^{1b}_p}},  
				{{\Post^{1b}_p}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha^1_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$
such that  $\Pred^1_p \iff {\Pred^{1a}_p}
		\land {\Pred^{1b}_p}\land \alpha^1_p=\beta^1_{pj_0}$, $\Post^1_p={\Post^{1a}_p}\uplus 
		{\Post^{1b}_p}$ where ${{\Post^{1b}_p}}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred^{1a}_p},  
				{\Post^{1a}_p}}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

@@

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred^a,  
				\Post^a}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{ij}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{ij}}
\\
\Pred^{a}=\big(\bigwedge_{i=0}^{m_1}
{\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
\land{\Pred^{2a}}\bigotimes_{i=0}^{m_1}\subst{{\Post_i^{1a}}}\land \\
~~\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big)\\
\Post^a=\bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}
$

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
$\forall p\! \in\! [0..(n_k'\!-\!1)] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
				{{\Post_p^{1b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
				{{\Post^{2b}}}}
				{\ostate{v_{n_k'l}^{l\in L_Q}} \OTarrow {\alpha'_k}
				\ostate{v_{(n_k'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n_k'\!+\!1)..(n_k\!-\!1)]\,\, Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
				{{\Post_p^{3b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma'_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
				{{\Post^b_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in  (J\cap\Holes(Q)),\,
\displaystyle{\gamma'_{kj} }=\mybigdotcup_{i=0}^{(n_k'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n_k'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
\\
\Pred^b_k=\Big(\!\!\!\bigwedge_{i=0}^{(n_k'-1)}\!\!
{\Pred_i^{1b}}\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^{1b}}}\Big)
\land\Big({\Pred^{2b}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\land\\
~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n_k'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\\
\Post^b_k=\bigotimes_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)
$\\

>>>>

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~~and~~}
%\[
Q\models{\openrule
	{
		\beta_j^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\TODO{important comment added:}
Note that this does not mean that any two pNets can be composed and produce an open 
transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is not 
be satisfiable if the action of $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
Note also that $\beta_{j_0}$ is now only used as an intermediate term inside formulas: it 
does not appear neither as global action nor as an action of a hole.
\begin{small}

@@

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $\gamma_{j_0}=[\beta_0..\beta_n]$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p= \beta_p\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i) 
\\
\text{and~}
\Post=\Post\,' \uplus \bigotimes_{p=0}^n
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

@@

\noindent We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred^{1a}_p},  
				{\Post^{1a}_p}}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^{1b}_p}},  
				{{\Post^{1b}_p}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha^1_{p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$
such that  $\Pred^1_p \iff {\Pred^{1a}_p}
		\land {\Pred^{1b}_p}\land \alpha^1_p=\beta^1_{pj_0}$, $\Post^1_p={\Post^{1a}_p}\uplus 
		{\Post^{1b}_p}$ where ${{\Post^{1b}_p}}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred^{1a}_p},  
				{\Post^{1a}_p}}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q\setminus L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

@@

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$\\
$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},
\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{ij}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{ij}}
\\
\Pred\,'=\big(\bigwedge_{i=0}^{m_1}
{\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
\land{\Pred^{2a}}\bigotimes_{i=0}^{m_1}\subst{{\Post_i^{1a}}}\land \\
~~\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big)\\
\Post'=\bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}
$

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition). By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.  We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
$\forall p\! \in\! [0..(n_k'\!-\!1)] Q\models{\openrule
			{
				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
				{{\Post_p^{1b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
				{{\Post^{2b}}}}
				{\ostate{v_{n_k'l}^{l\in L_Q}} \OTarrow {\alpha'_k}
				\ostate{v_{(n_k'+1)l}^{l\in L_Q}}}
				}%\]
$
and
$\forall p \in [(n_k'\!+\!1)..(n_k\!-\!1)]\,\, Q\models{\openrule
			{
				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
				{{\Post_p^{3b}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
				{{\Post^b_k}}}
			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{v_{l}'^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
$\forall j \in  (J\cap\Holes(Q)),\,
\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n_k'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n_k'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
\\
\Pred_k=\Big(\!\!\!\bigwedge_{i=0}^{(n_k'-1)}\!\!
{\Pred_i^{1b}}\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^{1b}}}\Big)
\land\Big({\Pred^{2b}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\land\\
~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n_k'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\\
\Post_k=\bigotimes_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)
$\\
